### 2024-03-28 docs/projects/geography/chicago-bikes/index.qmd
Chicago bikes - rerendered

# Chicago bikes

This page will be updated soon.

>>>>

# Analysing Chicago bike trips

This notebook is the fruit of our explorations at the new
[real-world-data group](https://scicloj.github.io/docs/community/groups/real-world-data/).
It uses a few of libraries of the emerging Clojure stack for data and science:
Tablecloth, dtype-next, Fastmath, Hanami, Geo, and Kindly.

Soon we will publish a video walkthrough.

Daniel Slutsky, March 2024
